Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-03-09 paper.tex
make summary

    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

@@

        A few extensions have also been added to the library in order to 
        improve user experience. An important extension is the introduction 
        of a \textit{combiner}, which enables the commutative and associative 
        reduce function to be applied to the same keys on the hosts where the 
        \textit{map} task was executed. Like the \textit{map} task, the 
        \textit{combiner} produces intermediate output which is sent to the 
        \textit{reducer}. This alleviates the amount of key-value pairs that 
        must be transferred over the network from the map host to the reduce 
        host, and as a result, improves performance. Other extensions include 
        the ability to create user-defined partitioning functions, a guaranteed 
        increasing key sort order, the ability for the user to specify input 
        types, an option to skip records that continuously result in execution 
        failure, the ability to produce auxiliary output files in \textit{map} 
        or \textit{reduce} task, live status updates stream to HTTP server,
        the ability to run all code on a single local machine, and a 
        \textit{Counter} class.
    \section{spark} 
        \begin{itemize} 
            \item based on map-reduce 
            \item in-memory processing 
            \item lazy evaluation 
            \item general framework 
        \end{itemize} 
     \section{Use of containers with Big Data frameworks}
     \section{Hadoop Distributed file system} 
        \note{maybe should go in between mapreduce and spark}

@@

\chapter{Scientific workflows in Spark}
    \section{Introduction}
    emphasis on data rather than on interface. transformation describe how
interfaces interact with the data. 
    \section{ariel's paper and thunders astronomy - }
    \section{Spark on hpc's or } 
        \note{large dataset for valduriez} Prior to
examining how Big Data frameworks could be improved on HPC clusters, it is
important to have a baseline of how it performs natively on an HPC cluster.
Particularly, how it behave when processing scientific workflows. In a recent
study done by \cite{valduriez}, they examined the scalability of Spark on an HPC
cluster using a black-box scientific workflow. Five tests were performed in
their study: 1) Measuring execution time when task and resources available
increase proportionally, 2) Measuring the execution time of very short and short
tasks, 3) Measuring the execution time of short (5s) to long tasks (120s), 4)
Varying the number of tasks with fixed task durations, 5) Mixed task durations
and varied number of tasks. Their results show Spark behaves as expected when
tasks and resources are increased exponentially, and that Spark scales better
than expected with tasks of longer durations. This is due to the fact that the
scheduler is overloaded in the case of many short tasks in addition to their
being a significant amount of I/O occurring between each task. Although I/O is
problematic in both data center and HPC infrastructures, HPC is optimized for
data transfer over the network rather than disk I/O, and therefore, such
frequent I/O negatively impacts the system. However, many scientific workflows
are composed of longer tasks, and therefore, Spark scales very well with
scientific workflows in an HPC environment.

@@

    In an attempt to improve performance of HDFS on HPC clusters, Triple-H was
created.  \section{Why is use of such systems important} \section{Scheduling}
\subsection{HPC schedulers: SLURM/QSUB} \subsection{Big Data schedulers:
YARN/MESOS} \subsection{Multi-level scheduling w/ BigData schedulers}
\chapter{Current status of Big Data frameworks in neuroscience} \section{Ariel's
paper} \section{Thunder} \chapter{Conclusion}

>>>>

    \section{Make}
        \subsection{Summary}
        As the creation of workflow activities requires a certain level of
programming expertise, Make was proposed as a simpler alternative. Make is a
tool used for the development of directed acyclic dependency graphs. It is
available in all Linux and UNIX distributions, which relieves the users from
worflow engine installation. Additionally, Make is capable of offering other
features necessary to workflow engines, such as, reproducibility,
parallelization, fault-tolerance and quality control. The motivation behind Make
is essentially that the tools available for simple and efficient pipeline
creation already exist and there is no need to 'reinvent the wheel'. In
addition, the use of Make is not limited to the neuroimaging community, and thus
support for it is widely available. Make has also been adapted for use in other
programming languages such as SnakeMake for python

        \subsection{Pipeline description}
        Make pipelines are described in makefiles, which consist of a set of
rules which describe the flow of data. Rules defined in make can be define by three
components: targets, dependecies and recipes. The target is the output
(typically file) produced by execution of the recipe, whereas the dependecy
would be the input file from which the target would be created from. The target
is only modified if its last modified date is early than that of a depencies's.
A recipe, in make, is the set of shell commands used to create the target from
its dependencies.

In order connect the rules together, it is possible to define "phony" targets.
Phony targets do not correspond to any actual file and will be generated once
all of their dependencies (targets of other rules) have been
created. Chaining multiple rules together will automatically generate the directed acyclic
graph that is the pipeline. This is contrary to other pipelines such as Nipype
and LONI, in which the user must explicitly state all connections \note{as
stated in paper}. Through the use of rules, it is easily possible to reexecute
only the desired parts of the pipeline.

Cleanup after rule execution can be defined using the phony target
clean.

To create different targets for the same dependency files organized in different
ways (e.g. subject/timpepoint timepoint/session), it is possible to use symbolic
links for the dependencies, however this may complexify the code. Otherwise, it
may be simpler to copy subject and session makefiles.

        Compared to the previous workflow engines, Make pipeline variables are
only evaluated at time of use (lazy evaluation). In addition, targets are not
executed in the order they are specified (similarly to other pipeline engines).

Make files are also well-equipped to handle workflows with conditionals. Should
a conditional exist in a workflow, it will be evaluated during the creation of
the DAG (i.e. not at runtime) and only the required components will be executed.

        As parallelism can be inferred from the dependency graph, parallel execution of a make pipeline can occur simply through the
addition of the -j flag for multicore machines, or by using qmake command to run
the pipeline on a cluster.

        By default, make only rebuilds targets whose last modified preceedes
that of its dependencies. As such, when a task fails and is re-executed, only the targets that need
to be rebuilt will be rebuilt. It is possible to specify reexcution in Make such
that the task will be reexecuted in case of failure.

        \subsection{Debugging and provenance}
        As users of a preexisting Make pipeline may not be aware of the proper
usage of each target, it is necessary to provide a `help` module that is
adaptable to targets being added removed or modified. It is possible to define
in Make a macro for such a purpose that will provide users with usage
information when requested (e.g. calling make help).

    Debugging in Make can be rather difficult, particularly when executing code
in parallel. However, pipelines in Make are broken down into many targets which
can each be tested individually. In addition, Make provides built-in flags to
aid in debugging. These flags include -n, for printing out the commands without
any execution and -p to print out all the rules. In the instance where pattern
substistution is used, -p will also include the results obtained from the
pattern substitution. More recent versions of GNU Make also include the --trace
and --output-sync flags which display why each recipe was executed and print the
parallelized output in sequential order, respectively.

    Neuroimaging tools are typically equipped with quality assurance modules. As
a result, it is possible to utilize the quality assurance modules from these
tools to provide a complete report for the entire pipeline. The proposed
solution suggests to write all the quality assurance outputs from each tool to a single HTML
report with R Markdown or a script. The R Markdown or script, with the metrics
and images are listed as dependencies to the QA report target in Make.

    Only a basic form of data provenance has been implemented by the authors.
The implemented data provenance consisted of a makefile that calls a bash to
extract acquisition parameters from the raw input images. The makefile also
obtains tool versions from the installation directories and pipeline options
from their respective makefiles. All of these details are stored in a CSV file.
The makefile will then call an R Markdown script which will then generate an
HTML provenance report from the corresponding CSV file.

    \section{Pydiper}
        \subsection{Summary}
        atoms -  wrappers for distinct operations
        modules - link atoms together
        applications - command line interface to the pipeline
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

@@

        A few extensions have also been added to the library in order to 
        improve user experience. An important extension is the introduction 
        of a \textit{combiner}, which enables the commutative and associative 
        reduce function to be applied to the same keys on the hosts where the 
        \textit{map} task was executed. Like the \textit{map} task, the 
        \textit{combiner} produces intermediate output which is sent to the 
        \textit{reducer}. This alleviates the amount of key-value pairs that 
        must be transferred over the network from the map host to the reduce 
        host, and as a result, improves performance. Other extensions include 
        the ability to create user-defined partitioning functions, a guaranteed 
        increasing key sort order, the ability for the user to specify input 
        types, an option to skip records that continuously result in execution 
        failure, the ability to produce auxiliary output files in \textit{map} 
        or \textit{reduce} task, live status updates stream to HTTP server,
        the ability to run all code on a single local machine, and a 
        \textit{Counter} class.
    \section{spark} 
        \begin{itemize} 
            \item based on map-reduce 
            \item in-memory processing 
            \item lazy evaluation 
            \item general framework 
        \end{itemize}

    \subsection{Scientific workflows in Spark}
        \subsubsection{Introduction}
        emphasis on data rather than on interface. transformation describe how
    interfaces interact with the data. 
        \subsubsection{ariel's paper and thunders astronomy - }
        \subsubsection{Spark on hpc's or } 
            \note{large dataset for valduriez} Prior to
    examining how Big Data frameworks could be improved on HPC clusters, it is
    important to have a baseline of how it performs natively on an HPC cluster.
    Particularly, how it behave when processing scientific workflows. In a recent
    study done by \cite{valduriez}, they examined the scalability of Spark on an HPC
    cluster using a black-box scientific workflow. Five tests were performed in
    their study: 1) Measuring execution time when task and resources available
    increase proportionally, 2) Measuring the execution time of very short and short
    tasks, 3) Measuring the execution time of short (5s) to long tasks (120s), 4)
    Varying the number of tasks with fixed task durations, 5) Mixed task durations
    and varied number of tasks. Their results show Spark behaves as expected when
    tasks and resources are increased exponentially, and that Spark scales better
    than expected with tasks of longer durations. This is due to the fact that the
    scheduler is overloaded in the case of many short tasks in addition to their
    being a significant amount of I/O occurring between each task. Although I/O is
    problematic in both data center and HPC infrastructures, HPC is optimized for
    data transfer over the network rather than disk I/O, and therefore, such
    frequent I/O negatively impacts the system. However, many scientific workflows
    are composed of longer tasks, and therefore, Spark scales very well with
    scientific workflows in an HPC environment.
     \section{Use of containers with Big Data frameworks}
     \section{Hadoop Distributed file system} 
        \note{maybe should go in between mapreduce and spark}

@@

@@

    In an attempt to improve performance of HDFS on HPC clusters, Triple-H was
created.  \section{Why is use of such systems important} \section{Scheduling}
\subsection{HPC schedulers: SLURM/QSUB} \subsection{Big Data schedulers:
YARN/MESOS} \subsection{Multi-level scheduling w/ BigData schedulers}
\chapter{Conclusion}
